\Title

### 2020-04-08 manuscript/manuscript.tex
Better description of relative depths

In the present study, we will evaluate the impact of different source
distributions, both horizontally and vertically, on the performance of
equivalent source interpolation.
Vertically, the sources can be located: (i) at a constant depth, (ii) at a
depth proportional to the height of observations, and (iii) at a depth
proportional to the median distance to adjacent data points.
The horizontal source distribution strategies are: (i) regular grid, (ii)
beneath data point, (iii) on the median location of data points inside spatial
blocks. The latter is a novel method while the others have been used in some
form in the past.

>>>>

In the present study, we will evaluate the impact of different source
distributions, both horizontally and vertically, on the performance of
equivalent source interpolation.
Vertically, the sources can be located: (i) at a constant depth, (ii) at a
depth relative to the height of observations, and (iii) at a depth
proportional to the median distance to adjacent data points.
The horizontal source distribution strategies are: (i) regular grid, (ii)
beneath data point, (iii) on the median location of data points inside spatial
blocks. The latter is a novel method while the others have been used in some
form in the past.
